A Flexible Space-time Tradeoff on Hybrid Index with Bicriteria Optimization

### 2016-07-17 manuscript.tex
day 3: Sec Intro finished

This idea is first adopted in \cite{yan2009inverted}.
However, the procedure of choosing encoders works at a posting list granularity, which is too coarse to obtain a flexible space-time tradeoff.
They also fail to explore complexity of the algorithm as it works on a empirical foundation.
Giuseppe et al. \cite{ottaviano2015optimal} explicitly define the Space-Constrained Expected Time Minimization problem: given a dataset $ D $ and an upper bound $ \cal S $ on its compressed size, the goal is to choose one proper encoder from an encoder set $ \cal E $ for each block of the index.
Thus minimizing the expected query processing time, provided that it can be compressed within $ \cal S $ space.

{\color{red}{how giuseppe does and what's the difference}}

>>>>

This idea is first adopted in \cite{yan2009inverted}.
However, the procedure of choosing encoders works at a posting list granularity, which is too coarse to obtain a flexible space-time tradeoff.
They also fail to explore complexity of the algorithm as it works on a empirical foundation.
Giuseppe et al. \cite{ottaviano2015optimal} explicitly define the Space-Constrained Expected Time Minimization problem: given a dataset $ D $ and an upper bound $ \cal S $ on its compressed size, the goal is to choose one proper encoder from an encoder set $ \cal E $ for each block of the index.
Thus minimizing the expected query processing time, provided that it can be compressed within $ \cal S $ space.
They then propose a linear time solution for this problem, which is quite straight forward.
Under two predefined dominance criteria, their algorithm works by enumerating all the advisable compression methods, then sorting them in an non decreasing order by the time/space gain ratio of each advisable encoder on each block.
After this, a sequential scan and replace is able to find all the optional solutions for any possible budget constraint $ \cal S $.
Given the fact that each posting list is divided into fixed-sized blocks (say, 128 postings) and a set of $ k $ encoders, the algorithm finishes in $ \Theta(nk\log(nk)) $ time and $ O(nk) $ space.

By refining the granularity to block level and the carefully designed algorithm, they are able to find a solution with minimal query time.
Also, the approximation is additive, which is at most a block size larger than $ \cal S $.
However, the algorithm takes too much space to sort the compression options that it can be hardly fit into memory; second, since the sorting and sequential scan cannot be accelerated by parallel, the whole procedure is delay by them somehow; third, their solution is based on assumption that the posting lists are split into fixed-sized blocks, otherwise the compression options are hardly to sort and might take much more space.

We argue that global ordering of the compression options for all the blocks is not a good idea, since it will lead to the above three shortcomings.
In this paper, we try to attack this problem from another perspective.
The main contributions are listed below:
\begin{enumerate}
	\item We introduce the conception of \textit{Bicriteria Compression} problem \cite{farruggia2014bicriteria} to extend the Space-Constrained Expected Time Minimization problem, which contains another dual problem.
	It changes the role of space/time by asking for the minimal compressed size, provided an upper bound $ T $ in its average query processing time or decompression time.
	By solving the \textit{Bicriteria Compression} problem  we can expect our compression method to be more universal for different scenarios.
	\item We reduce the problem into a Resource Constrained Shortest Path problem \cite{mehlhorn2000resource} over a weighted DAG $ \cal G $, however, edges in $ \cal G $ contain two penalties: space cost and time weight.
	Thus, the problem can be formalized using Lagrangian relaxation, we use the algorithm introduced in \cite{farruggia2014bicriteria} and \cite{handler1980dual} to settle in $ O(n\log^{2}n) $ time and $ O(n) $ space, while keeping the same additive approximation guarantee.
	\item Different from \cite{ottaviano2015optimal} which is a global search algorithm, our method amortizes the expect budget over each posting list.
	Thus, all the phrases of compression can be processed in a parallel way, runtime space requirement is also reduced without storing options in an index level.
	Our method is able to keep the additive approximation guarantee under different budgets, however, works much faster in practice.	
	{\color{red} Use data to demonstrate it}.
	\item we execute a preliminary set of experiments on two realistic dataset, GOV2 and Common Crawl, with AOL query log.
	Analysis shows that our method is able to obtain flexible tradeoffs under bicriteria compression.
	Its compressed size and query processing time is very competitive to the hybrid index in \cite{ottaviano2015optimal}, however, with more detailed description and more strict theoretic foundation.
\end{enumerate}
